Ornaments as indicators of social changes in northeastern Taiwan before and after the European colonial period

### 2020-04-28 analysis/paper/paper.Rmd
add sentences about spatial analysis in point pattern section

Point pattern analysis can assess whether the distribution of artifacts represents hotspots produced by non-random processes [@Bevan2016; @Ducke2015], such as concentrations of ornaments in specific households that might result from social inequality stimulated by a colonial presence. To prepare the ornament location data for point pattern analysis, because artifacts from Kiwulan lack exact piece-provenance data, we assigned each ornament to a random coordinate pair in the square it was recovered from. The next step was to divide the ornaments into three time periods. Finally we computed the kernel densities for each time period for comparison. Kernel density estimations (KDE) compute the probability of the density of ornaments across space by creating a continuous, smooth density surface across space. Here we use KDE to visualize core areas of ornaments and surrounding neighborhoods [@Bonnier2019; @Cortegoso2016]. Density values of artifacts per square meter were calculated for each cell.

>>>>

The distribution and density of prestige goods across the residential area can provide information of social structure based on the assumption that distribution patterns observed from spatial data can reveal cultural processes by statistical methods [@Kintigh1982]. Point pattern analysis can assess whether the distribution of artifacts represents hotspots produced by non-random processes [@Bevan2016; @Ducke2015], such as concentrations of ornaments in specific households that might result from social inequality stimulated by a colonial presence. To prepare the ornament location data for point pattern analysis, because artifacts from Kiwulan lack exact piece-provenance data, we assigned each ornament to a random coordinate pair in the square it was recovered from. The next step was to divide the ornaments into three time periods. Finally we computed the density maps for each time period for comparison. Density values of artifacts per square meter were calculated for each cell. Here we use Kernel density estimations (KDE) for visualization and identification of spatial clusters [@Baxter1997], the core areas of ornaments and surrounding neighborhoods in this case. KDE is a approach of spatial analysis that computes the probability of the density of ornaments across space by creating a continuous, smooth density surface across space [@Bonnier2019; @Cortegoso2016].
